Examining the Influence of Premises Type and Time of Day on Violent Crime in Toronto

### 2024-12-03 paper/paper.qmd
updates to survey

@@

This questionnaire is designed to collect detailed information from victims of violent crimes. The sections and questions align precisely with the Google Form provided. Additionally, attention checks have been included in the survey to ensure data quality. The survey is accessible at the following link:  
[https://forms.gle/d81J3S9HpPgJPUkM6](https://forms.gle/d81J3S9HpPgJPUkM6)

@@

### Informed Consent

- Participants will receive detailed information about the study's purpose, procedures, risks, and benefits.
- Consent forms will be signed prior to participation.
- Participants can withdraw at any time without penalty.

### Confidentiality

- Personal identifiers will be removed or coded.
- Data will be stored securely with access limited to authorized personnel.
- Results will be reported in aggregate to prevent identification.

### Protection of Participants

- Interviews will be conducted sensitively to minimize distress.
- Referral information for support services will be provided.
- Participation is entirely voluntary.

### Ethical Approval

The study protocol will be reviewed and approved by an Institutional Review Board (IRB) or Research Ethics Board (REB) prior to commencement.

@@

### Mode of Data Collection

- **Primary Method**: Telephone interviews conducted by trained researchers.
- **Alternative Methods**: In-person interviews or online questionnaires, depending on participant preference.

### Interviewer Training

- Training on trauma-informed interviewing techniques.
- Guidelines on handling disclosures and providing support information.

### Timeline

Data collection will occur within two months following the incidents to ensure accurate recall.

### Contact Protocol

- Initial contact will be made via mail or email explaining the study and requesting participation.
- Follow-up contact will be made to schedule interviews.

@@

@@

# Import the simulated data from the specified CSV file
simulated_data <- read_csv(here::here("data/00-simulated_data/survey_simulated_crime_data.csv"))

>>>>

## Budget Allocation

The total budget for this survey is $100,000, allocated as follows:

- **Recruitment and Outreach ($25,000):**
  - Partnering with Toronto Police Services to contact victims via official channels.
  - Direct mailers and digital outreach (e.g., SMS, emails).

- **Incentives for Participation ($60,000):**
  - $20 gift card for completing the survey.
  - Estimated 3,000 participants.

- **Survey Design and Implementation ($10,000):**
  - Professional survey platform subscription.
  - Data cleaning and preprocessing costs.

- **Contingency Funds ($5,000):**
  - Unanticipated costs related to participant recruitment or data handling.

This allocation prioritizes participant incentives to ensure robust response rates while maintaining sufficient funding for recruitment and operational expenses.

@@

The questionnaire is designed to collect detailed information from victims of violent crimes. Attention checks are included to ensure data quality. The survey link: [Survey Form](https://forms.gle/d81J3S9HpPgJPUkM6).

@@

### Informed Consent
- Participants will be informed about the purpose, risks, and benefits of the survey. Consent is mandatory.

### Confidentiality
- Responses will be anonymized. Data will be securely stored and used only for research purposes.

### Protection of Participants
- Sensitive topics will be handled by trained staff. Resources for support services will be provided.

### Ethical Approval
- The study protocol will undergo review by a Research Ethics Board (REB).

@@

### Mode of Data Collection
- **Primary Method**: Online surveys through a secure platform.
- **Alternative Methods**: Telephone interviews for participants with limited internet access.

### Timeline
- Data collection will be completed within two months of the survey launch.

### Contact Protocol
- Initial invitations via email or mail, followed by reminders to maximize participation.

@@

```{r}
#| label: tbl-simulated-data
#| tbl-cap: "Preview of the Simulated Crime Dataset"
#| echo: false
#| warning: false
#| message: false

simulated_data <- read_csv(here::here("data/00-simulated_data/survey_simulated_crime_data.csv"))

# Transpose the first 5 rows of the dataset
t_simulated_data <- simulated_data[1:5, ] %>%
  t() %>%
  as.data.frame()

# Convert row names to a column for display
t_simulated_data <- tibble::rownames_to_column(t_simulated_data, var = "Variable")

# Display the transposed data with variables on the left
t_simulated_data %>%
  kable()
```

@@
